An agent-based model of military mechanization

### 2018-07-08 paper2/paper2.tex
thinking

Methodology studies
\citep{pepinsky2005agents,de2014agent,gunitsky2013complexity,bousquet2011beyond,harrison2012complexity,jervis1998system,modelski1990world,modelski1999long}

@@

@@

\begin{table}[h]
	\centering
	\caption{Comparison}
	\begin{tabular}{|l r r|}
		\hline
		\textbf{Year} & \textbf{Model} & \textbf{Reality} \\
		1979 & 0.0156 & 0.0139 \\
		1981 & 0.0189 & 0.0167 \\
		1983 & 0.0229 & 0.0167 \\
		1985 & 0.0280 & 0.0183 \\
		1987 & 0.0351 & 0.0187 \\
		1989 & 0.0415 & 0.0197 \\
		1991 & 0.0512 & 0.0215 \\
		1993 & 0.0636 & 0.0229 \\
		1995 & 0.0804 & 0.0231 \\
		1997 & 0.1014 & 0.0270 \\
		1999 & 0.1319 & 0.0272 \\
		2001 & 0.1730 & 0.0291 \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[h]
	\centering
	\caption{Mexico}
	\begin{tabular}{|l r r|}
		\hline
		\textbf{Year} & \textbf{Model} & \textbf{Reality} \\
		1979 & 0.0013 & 0.0012 \\
		1981 & 0.0014 & 0.0012 \\
		1983 & 0.0018 & 0.0026 \\
		1985 & 0.0019 & 0.0013 \\
		1987 & 0.0021 & 0.0019 \\
		1989 & 0.0022 & 0.0027 \\
		1991 & 0.0024 & 0.0030 \\
		1993 & 0.0026 & 0.0033 \\
		1995 & 0.0030 & 0.0035 \\
		1997 & 0.0032 & 0.0074 \\
		1999 & 0.0036 & 0.0082 \\
		2001 & 0.0040 & 0.0075 \\
		\hline
	\end{tabular}
\end{table}

>>>>

Methodology studies
\citep{pepinsky2005agents,de2014agent,
gunitsky2013complexity,bousquet2011beyond,
harrison2012complexity,jervis1998system,modelski1990world,modelski1999long,cederman2001agent}

@@

Cite Cederman to say why I don't do inheritenace - reification of actor

Why ABM:
 - inadequacy of SS - VIF, linear model
 - uncertainty of causation
 - endogeneity
 - GDP / capita explains this...but also everything else
 - have to go with simulation
 - bigger picture, world politics as complex system
 - look at Axtell \citep{axtell2000agents}

@@

\begin{table}[h]
	\centering
	\caption{Comparison}
	\begin{tabular}{|l r r r|}
		\hline
		\textbf{Year} & \textbf{Model} & \textbf{Reality} & \textbf{Difference}\\
		1979 & 0.0156 & 0.0139 & 0.0017 \\
		1981 & 0.0189 & 0.0167 & 0.0022 \\
		1983 & 0.0229 & 0.0167 & 0.0062 \\
		1985 & 0.0280 & 0.0183 & 0.0097 \\
		1987 & 0.0351 & 0.0187 & 0.0164 \\
		1989 & 0.0415 & 0.0197 & 0.0218 \\
		1991 & 0.0512 & 0.0215 & 0.0297 \\
		1993 & 0.0636 & 0.0229 & 0.0407 \\
		1995 & 0.0804 & 0.0231 & 0.0573 \\
		1997 & 0.1014 & 0.0270 & 0.0744 \\
		1999 & 0.1319 & 0.0272 & 0.1047 \\
		2001 & 0.1730 & 0.0291 & 0.1439 \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[h]
	\centering
	\caption{Mexico}
	\begin{tabular}{|l r r r|}
		\hline
		\textbf{Year} & \textbf{Model} & \textbf{Reality} & \textbf{Difference}\\
		1979 & 0.0013 & 0.0012 & 0.0001  \\
		1981 & 0.0014 & 0.0012 & 0.0002  \\
		1983 & 0.0018 & 0.0026 & -0.0008 \\
		1985 & 0.0019 & 0.0013 & 0.0006  \\
		1987 & 0.0021 & 0.0019 & 0.0002  \\
		1989 & 0.0022 & 0.0027 & -0.0005 \\
		1991 & 0.0024 & 0.0030 & -0.0006 \\
		1993 & 0.0026 & 0.0033 & -0.0007 \\
		1995 & 0.0030 & 0.0035 & -0.0005 \\
		1997 & 0.0032 & 0.0074 & -0.0042 \\
		1999 & 0.0036 & 0.0082 & -0.0046 \\
		2001 & 0.0040 & 0.0075 & -0.0035 \\
		\hline
	\end{tabular}
\end{table}
